% !Mode:: "TeX:UTF-8"

\begin{Eabstract}{Voice Calling System}{Embedded System}{Upper-side Machine}{Database}{TCP/IP}
Hospital voice calling systems are important tools and means of hospital management, to improve medical quality to promote resource sharing and improving competitiveness is of great significance.

The subject of this article is derived from the author's career, the author's daily work involves very much contact with hospitals, and I found that hospitals currently use products in their daily work, there are many areas that need improvement. Existing management system is used in most hospital wards localized management need to be constructed to ward visits, observation patients, reducing the efficiency of work. With the growing health concerns, increasing medical practice leads to the decrease hospital system performance, management system can no longer meet in hospital wards are now busy business systems. With the development of network people increasingly rely on Internet technology brought convenience to people, but also the background of the system design.

This thesis analyses the development status of the voice calling system of the hospital ward, noted that shortcomings of the calling system, and according to the specific business needs of the hospital ward of an improved voice calling system solutions. This programme is divided into two parts: embedded systems and PC software system, embedded system hardware to STM32 controlled Finish button response, audio capture and playback, Internet access and other features; RT-Thread based embedded real-time operating system for embedded systems software development, responsible for embedded system hardware drivers and management.

PC software in accordance with the functions of the system can be divided into four major business function modules and three management modules, and describes the various functional modules of typical business. Using object-oriented programming techniques to abstract the system requirements, complete PC software architecture design, final integrated development environment using Visual C{\#} complete system design and implementation. Finally, the system introduces the software installation, deployment, configuration, and functional integrity, accuracy and stability of the system was tested, test results show that the relative can meet Hospital demand for voice calls, greatly enhance the efficiency of management of hospital wards.
\end{Eabstract}
